\section{Description}
\subsection{Product Perspective}
The game is intended to be built in the desired OS with a peer-to-peer (P2P)
networking implementation. The game will communicate with servers in order to
facilitate the creation and maintenance of this environment necessary to play
checkers. The actual game that is being played will be displayed to both
players in realtime. The game will be represented graphically.

\subsection{Product Functions}
\subsubsection{Workstation Functionality}
The workstation refers to the system on which the program is initialized and
ran by the users who intend to play this game. The workstation will be able to
connect to a network in order to communicate with the server. The workstation
will display the checkers board in its current state to the two current
workstations being operated by the active users.

\subsubsection{Server Functionality}
Clients act as servers as well as their main operation as clients, due to the
P2P nature of this implementation. The main purpose of the server will be to
conduct matchmaking services. The server will ensure that an environment is
created in which two players are able to join each other in order to play a
game of checkers with one another. The server will be successful if a game
session can be hosted with no errors, issues or crashes to completion.  The
server will also ensure  that the rules of the game that is being played are
followed to prevent any illegal moves by a player. The server must be
accessible at all times over a network in order to ensure that the game can be
played from differing remote locations.

\subsection{User Description}
The users of the product will be composed of two persons, separated by some
distance, who launch the application with the desire to play checkers via a
networked connection.  Any two random users may be playing against one another
at any point. The purpose of the program is to create a piece of software/game
that ensures that no physical connection is required between the two “active”
users as there may be users within the game that may be present but inactive
thereby rendering their status as idle.

\subsection{Assumptions \& Dependencies}
\subsubsection{OS Support}
The game is being designed with portability and some ``cross-platform support''
in order to ensure that the software will run efficiently regardless of the OS
on which it is executed on. Assuming the code written is error free, no
instance should occur in which there is a crash due to the operating software.
We will also assume that the program is being executed on a functional system
with a stable internet connection.

\subsubsection{Docker}
The game is being built with Docker in order to build and manage the different
dependencies in a manner that is independent of the host system. Allows for
easy, across-the-board modifications as well as a containment of modules being
written.

\subsubsection{GNU Make}
To ease development efforts, \textt{make} will be used to build and execute the
many commands that are necessary to create and maintain a build.
