\section{Functional Requirements}

\subsection{Game Logic}
\begin{itemize}
  \item Play a game of checkers
  \item Only allow correct moves
  \item Only allow each player to move when it's their turn
  \item End the game when a win condition is met
  \item Play over two computers via the internet
  \item Allow player clients to connect without a server (peer-to-peer)
  \item Display the game's current board on each players screen
  \item At start up display a box to type in the opponents IPv4 address
  \item Players can move pieces of the game with their mouse
\end{itemize}

\subsubsection{Playing a Game}
\paragraph{Rules:}
The game is played on a common chess board, although traditionally the checker
boards use black and red of the squares. A game is played with 2 players one
controls the white pieces and one controls the black pieces. Each player has
control of 12 pieces. Pieces are initally placed on the black squares of the
first three rows for each side of the board.

\paragraph{Game Board:}
\subparagraph{Key:}{%
  \begin{itemize}
    \item \texttt{\#} is a black square
    \item \textt{o} is a red square
  \end{itemize}
}
\begin{tabular}{|c|c|c|c|c|c|c|c|}
  \hline
  \multicolumn{8}{|c|}{White Side}  \\ \hline
  o & \# & o & \# & o & \# & o & \# \\ \hline
  \# & o & \# & o & \# & o & \# & o \\ \hline
  o & \# & o & \# & o & \# & o & \# \\ \hline
  \# & o & \# & o & \# & o & \# & o \\ \hline
  o & \# & o & \# & o & \# & o & \# \\ \hline
  \# & o & \# & o & \# & o & \# & o \\ \hline
  o & \# & o & \# & o & \# & o & \# \\ \hline
  \# & o & \# & o & \# & o & \# & o \\ \hline
  \multicolumn{8}{|c|}{Black Side}  \\ \hline
\end{tabular}

\paragraph{Inital Setup}
\subparagraph{Key:}{%
  \begin{itemize}
    \item \texttt{\#} is a black square
    \item \texttt{o} is a red square
    \item \texttt{b} is a black piece
    \item \texttt{w} is a white piece
  \end{itemize}
}
\begin{tabular}{|c|c|c|c|c|c|c|c|}
  \hline
  \multicolumn{8}{|c|}{White Side}      \\ \hline
  o  & w  & o  & w  & o  & w  & o  & w  \\ \hline
  w  & o  & w  & o  & w  & o  & w  & o  \\ \hline
  o  & w  & o  & w  & o  & w  & o  & w  \\ \hline
  \# & o  & \# & o  & \# & o  & \# & o  \\ \hline
  o  & \# & o  & \# & o  & \# & o  & \# \\ \hline
  b  & o  & b  & o  & b  & o  & b  & o  \\ \hline
  o  & b  & o  & b  & o  & b  & o  & b  \\ \hline
  b  & o  & b  & o  & b  & o  & b  & o  \\ \hline
  \multicolumn{8}{|c|}{Black Side}      \\ \hline
\end{tabular}

\subsubsection{Movement Rules}\label{subsec:movement-rules}
\begin{itemize}
\item
  Pieces can only move from black squares to other black squares.
\item
  There can not be another piece in the way for a piece to move there.
\item
  Pieces move diagnolly, normal pieces can usually move one square diagonally
  an only forward towards the other side. King pieces can more diagonolly one
  square but in either direction.
\item
  Pieces can capture the opponents pieces by \emph{jumping} over them.  Inorder
  to jump over a piece the jumper needs to be next to the piece it wants to
  jump over and there needs to be a space in the square on diagonally behind
  the piece which is being jumped over and captured.
\item
  King pieces can move both backwards and forwards.
\end{itemize}

\subsubsection{Capturing}
As explained in Movement Rules (\fullref{subsec:movement-rules}), pieces can
jump over opponent pieces to capture them. Once a piece is captured, it is
removed from the game. It is possible for multiple pieces to be captured in a
single move.

\paragraph{Key:}{%
  \begin{itemize}
    \item \texttt{\#} is a black square
    \item \texttt{o} is a red square
    \item \texttt{b} is a black piece
    \item \texttt{w} is a white piece
    \item \texttt{1} first jump
    \item \texttt{2} second jump
  \end{itemize}
}

\noindent
\begin{tabular}{|c|c|c|c|c|c|c|c|}
  \hline
  \multicolumn{8}{|c|}{White Side}  \\ \hline
  o & \# & o & \# & o & \# & o & \# \\ \hline
  \# & o & \# & o & \# & o & \# & o \\ \hline
  o & w & o & \# & o & \# & o & \# \\ \hline
  \# & o & b & o & \# & o & \# & o \\ \hline
  o & \# & o & 1 & o & \# & o & \# \\ \hline
  \# & o & \# & o & b & o & \# & o \\ \hline
  o & \# & o & \# & o & 2 & o & \# \\ \hline
  \# & o & \# & o & \# & o & \# & o \\ \hline
  \multicolumn{8}{|c|}{Black Side}  \\ \hline
\end{tabular}

\subsubsection{Kings}
Pieces become kings once they reach the opponents side.

\subsubsection{Win Conditions}
\begin{itemize}
  \item One player captures all of the opponents pieces (they win).
  \item A player is put into a position where they can not move (they lose, the
    other player wins).
  \item A player resigns (they lose, the other player wins).
\end{itemize}
Our software will end the game once a win condition is met and it will
display a message which tell which player has won the game. Once the
game is ended it will return to the main menu.

\subsubsection{Move Validation}
Players will only be able to input moves which are legal under specifications
of this document and as follows:
\begin{itemize}
  \item Players will not be able to move for the other player.
  \item Players will not be able to move onto their own pieces.
\end{itemize}

\subsection{Networking}
\subsubsection{Remote Play}
Players will be able to play against each other over the internet on two
seperate computer devices. This function will allow for two players to play
checkers remotely without requiring any kind of physical connection between
their computers.

\subsubsection{Peer-to-peer (P2P)}
Players will be able to connect their clients togther to play a game without
the need for a centralized server. Instead, they will simply have to share
their IPv4 addresses and than connect using the Interface.

\subsection{User Interface}
\subsubsection{Board Screen}
Our software will create a window with the operating's window system which
allows for the game board and pieces to be displayed in 3d on the screen of the
both players. It will update once a move is made. The screen will also have
buttons to resign, and exit.

\subsubsection{Startup Screen}
The startup screen will have a textbox to enter a players IPv4 address. It
will also display instructions and a checkers rules. Finally, there will be a
button to quit the software.

\subsubsection{IPv4 Address Selection}
In order to find a player to play against, the software will provide a textbox
accepting valid IPv4 address input. When two clients enter their respective IPv4
addresses, they will connected to each other, and a game will commence. There
will also be a text prompt which will display the status of the connection.
If no other player is found, the software will time out.

\subsubsection{Interface Interaction}
Inside the display window players will be able to click on pieces which they
would like to move and then click on the place where they would like to move.
The UI will show which moves are legally possible.

\subsubsection{Splash Screen}
On software start up a splash screen will show a screen with release build
information.
