\section{User Interface}

\subsection{Start Screen}
Upon starting the application, the user will be presented with a screen
displaying the title of the game.  The user will be prompted to press any key
to continue to the Main Menu Screen.

\subsection{Main Menu Screen}
The main menu will contain 4 buttons: Local Game, Internet Game, Exit Game, and
About.
\begin{itemize}
  \item The Local Game button will navigate the user to the Local Game Screen.
  \item The Internet Game button will navigate the user to the Internet Game Screen
  \item The Exit Game button will prompt the user for a confirmation and then exit the application.
  \item The About button will navigate the user to the About Screen.
\end{itemize}

\subsection{Local Game Screen}\label{subsec:local-game-screen}
The local game screen will contain 2 buttons: Host Game and Find Game.
\begin{itemize}
  \item
    The Host Game button will start the server application and create a
    ``lobby'' displayed on the same screen.
  \item
    The lobby will update as a new user joins. A new button labeled Start Game
    will appear to allow the host to start the game, navigating to the Main
    Game Screen.
  \item
    The Find Game button will search for the server application on local
    intranet and display the available servers as lobbies.
  \item
    Clicking on an available server will prompt the user for confirmation and
    transition the list of lobbies into a display of the current lobby.
\end{itemize}

\subsection{Internet Game Screen}
The Internet Game Screen shall contains 2 buttons: Host Game and Join Game.  A
button to navigate back to the previous screen will also be provided.
\begin{itemize}
  \item
    The Host Game button shall start the server application and display the
    host's IP Address. A lobby shall be displayed such as in the Local Game
    Screen (\fullref{subsec:local-game-screen}).
  \item
    The lobby shall update as a new user joins. A new button labeled Start Game
    shall appear to allow the host to start the game, navigating to the Main
    Game Screen.
  \item
    A text input box shall be displayed next to the Join Game button and take
    an IP address of host as input.
  \item
    The Join Game button shall validate input of the IP address text input and
    enter the host's ``lobby''.
\end{itemize}

\subsection{About Screen}
The about screen shall contains 4 buttons: How To Play, Application Info,
Credits, and Main Menu. A button to navigate back to the previous screen will
also be provided.

\begin{itemize}
  \item The How to Play button shall display the rules of the game to the user.
  \item The Application Info button shall navigate to the Application Info
    Screen.
  \item The Credits button shall navigate to the Credits Screen.
  \item The Main Menu button shall exit the game for both players and return to
    the Main Menu Screen.
\end{itemize}

\subsection{Credits Screen}
The credits screen will display the name of entities contributing to the
development of the application. A button to navigate back to the previous
screen will be provided.

\subsection{Application Info Screen}
The application info screen will display the application's version, patch
notes, and license information. A button to navigate back to the previous
screen will be provided.

\subsection{Main Game Screen}
The main game screen will display the game's current board on each player's
screen. Players can move pieces by clicking or touching the piece.  The board
shall appear as a standard drought 8$\times$8 grid of two contrasting,
alternating colors.
\begin{itemize}
  \item
    Main game screen will contain a Resign button which will prompt player for
    confirmation then transition into End Game Screen
  \item
    Once a piece is clicked, it shall be highlighted in one color.  All
    available moves for the highlighted piece shall be displayed in another
    color.
 \item
   Upon the completion of the opposing player's turn, text shall be displayed
   to indicate a new player's turn.
  \item
    Upon a win condition, a pop-up shall be displayed to players.  Pop-up will
    announce the winner and present both players with a Main Menu button to
    navigate to the Main Menu Screen.
\end{itemize}

\subsection{End Game Screen}
End game screen is Main Game Screen with interactions disabled and a banner
displaying the winner of the game.  End game screen will contain a Main Menu
button which will transition user to Main Menu Screen.
