\section{Use Cases}

\subsection{Movement}
To move a piece, click on the piece then click on a square highlighting a valid
move for said piece.  An unpromoted piece is only able to move in the forward
direction.

\subsection{Capturing}
To capture a piece, click on your capturing piece and then click on a square
highlighing an available capture move. As per drought rules, capturing when
possible is mandatory. An unpromoted piece can only capture in the forward
direction. A promoted piece can capture in either direction.
\begin{itemize}
  \item
    \textbf{Precondition:} An opponent's piece is located in a position
    available for capture (located on an adjacent diagonal).
  \item
    \textbf{Action:} Player indicates intention to move ``over'' an enemy
    piece.
  \item
    \textbf{Postcondition:} Player's piece has been moved behind the enemy
    piece (hops over the enemy piece) and enemy piece has been removed from the
    game.
\end{itemize}

\subsection{Promoting}
Moving a piece to the last opposing row will result in a promotion of said
piece.
\begin{itemize}
  \item
    \textbf{Precondition:} Unpromoted piece is able to move to last row of
    board.
  \item
    \textbf{Action:} A piece has completed a move to the last row of the board.
  \item
    \textbf{Postcondition:} Promoted piece is now able to move and capture in
    both the forward and backward directions.
\end{itemize}

\subsection{Game Completion}
When all of a player's pieces are captured, the game is complete. The player
with pieces on the board is the winner.
\begin{itemize}
  \item
    \textbf{Precondition:} Player has one piece on board.
  \item
    \textbf{Action:} Any player's final game piece is captured.
  \item
    \textbf{Postcondition:} Banner displays winner of game and a button to
    return to the main menu.
\end{itemize}

\subsection{Local Game Hosting}
\begin{itemize}
  \item
    \textbf{Precondition:} User is on Local Game Screen.
  \item
    \textbf{Action:} User clicks Host Game.
  \item
    \textbf{Postcondition:} Server application starts and is now able to
    recieve connections from a single other player client.
\end{itemize}

\subsection{Internet Game Hosting}
\begin{itemize}
  \item
    \textbf{Precondition:} User is on Internet Game Screen.
  \item
    \textbf{Action:} User clicks Host Game.
  \item
    \textbf{Postcondition:} Server application starts and is now able to
    recieve connections from a single other player client. IP Address of host
    is displayed.
\end{itemize}

\subsection{Local Game Starting}
\begin{itemize}
  \item
    \textbf{Precondition:} User has hosted a local game and a player has joined
    their lobby.
  \item
    \textbf{Action:} User clicks Start Game.
  \item
    \textbf{Postcondition:} Both players transition to Main Game Screen.
\end{itemize}

\subsection{Internet Game Starting}
\begin{itemize}
  \item
    \textbf{Precondition:} User has hosted an internet game and a player has
    joined their lobby.
  \item
    \textbf{Action:} User clicks Start Game.
  \item
    \textbf{Postcondition:} Both players transition to Main Game Screen.
\end{itemize}

\subsection{Resigning}
\begin{itemize}
  \item
    \textbf{Precondition:} User wishes to resign game and it is their turn.
  \item
    \textbf{Action:} User clicks Resign and confirms prompt.
  \item
    \textbf{Postcondition:} Both users transition into End Game Screen with
    resigning user being the loser.
\end{itemize}
